% !TEX encoding = UTF-8 Unicode
\documentclass[margin]{res}
\setlength{\textwidth}{5.1in}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\begin{document}
	\moveleft.5\hoffset\centerline{\large\bf Renan Domingos Merlin Greca}
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
	\moveleft.5\hoffset\centerline{\href{mailto:renangreca@gmail.com}{renangreca@gmail.com} - +55 41 9246-2128}
	\moveleft.5\hoffset\centerline{\href{https://github.com/RenanGreca}{github.com/RenanGreca}}

	\begin{resume}

		\section{EDUCATION}
			{\sl Universidade Federal do Paraná}, Curitiba-PR, Brazil. \\
			Master of Science, Computer Science. Conclusion in May/2018. \\
			{\sl Thesis title:} TruMan: Trust Management for Vehicular Networks \\\\
			{\sl Universidade Federal do Paraná}, Curitiba-PR, Brazil. \\
			Bachelor of Science, Computer Science. Conclusion in December/2015. \\\\
			{\sl Pomona College}, Claremont-CA, United States. \\
			Non-degree exchange student. From September/2013 to May/2014. \\\\
			{\sl Pontifícia Universidade Católica do Paraná}, Curitiba-PR, Brazil \\
			Brazil Education Program for iOS Development. From February/2015 to December/2015.
			
		\section{SKILLS AND \\ABILITIES}
			{\sl Programming Languages:}
			\begin{itemize}
	 			\item[] Swift, Objective-C, C, Python, Ruby, Java, JavaScript, PHP.
	  		\end{itemize}
%			{\sl Development Tools:}
%			\begin{itemize}
%				\item [] Xcode, RubyMine, PyCharm, PHPStorm, Android Studio, Bash, Git, Sublime Text, Vim, \TeX, MySQL, PostgreSQL.
%			\end{itemize}
%			{\sl Other Tools:}
%			\begin{itemize}
%	 			\item[] Microsoft Office, Adobe Photoshop, Adobe Lightroom, GarageBand. 	
%			\end{itemize}
%		    {\sl Operating Systems:}
%	 		\begin{itemize}
%	 			\item[] OS X, iOS, Linux, Windows, Android.
%	   		\end{itemize}
			{\sl Languages:}
			\begin{itemize}
				\item[] Native Portuguese, fluent English, intermediate German, basic Spanish.
			\end{itemize}

 		\section{EXPERIENCE}
 			{\sl CINQ Technologies}, Curitiba-PR, Brazil \hfill March/2018 - Present \\
 			Development Analyst
 			\begin{itemize}
				\itemsep -2pt
		    	\item iOS application maintenance and evolution.
			\end{itemize}
			Supervisor: Marcelo Wzorek, \href{mailto:m.wzorek@cinq.com.br}{m.wzorek@cinq.com.br}.
 		
			{\sl Malote Digital}, Curitiba-PR, Brazil \hfill October/2014 - July/2015 \\
			Jr. Programmer
			\begin{itemize}
				\itemsep -2pt
		    	\item Web application development.
				\item Responsible for finding and implanting tools for development, documentation and collaboration that would help the team.
			\end{itemize}
			Supervisor: Newton Tortorello, \href{mailto:tortorello@niti.com.br}{tortorello@niti.com.br}.
			
			{\sl Yahoo, Inc.}, San Francisco-CA, United States \hfill May/2014 - August/2014 \\
			Intern, Flickr.
			\begin{itemize}
				\itemsep -2pt
		    	\item Gathering of data for usage in an image recognition application with machine learning.
			\end{itemize}
			Supervisor: Jack Culpepper, \href{mailto:jackcul@yahoo-inc.com}{jackcul@yahoo-inc.com}.

%			{\sl New Ideas}, Curitiba-PR, Brazil \hfill February/2011 - August/2013 \\
%			Development Intern.
%			\begin{itemize}
%				\itemsep -2pt
%		    	\item Development of application in PHP, JavaScript, HTML and CSS.
%			\end{itemize}
%			Supervisor: Newton Tortorello, \href{mailto:tortorello@niti.com.br}{tortorello@niti.com.br}.
			
		\section{PERSONAL \\ PROJECTS}
			{\sl Nintendo Fusion} - \href{http://nintendofusion.com.br}{http://nintendofusion.com.br}.
			\begin{itemize}
				\item[] Co-founder, editor, web developer, systems administrator.
			\end{itemize}
%			{\sl Who's That Pokémon} - \href{https://whosthatpokemon.net}{https://whosthatpokemon.net}.
%			\begin{itemize}
%				\item[] Web-based game made with NodeJS and MongoDB.
%			\end{itemize}
			{\sl GameBlast} - \href{https://gameblast.com.br}{https://gameblast.com.br}.
			\begin{itemize}
				\item[] Director of audio and transmissions. Responsible for BlastCast and live programming.
			\end{itemize}
%			{\sl Shinesparkers} - \href{https://shinesparkers.net}{https://shinesparkers.net}.
%			\begin{itemize}
%				\item[] News and content writer.
%			\end{itemize}

		\section{PUBLICATIONS}
			\textbf{R. Greca}, L. C. P. Albini. {\sl TruMan: Trust Management for Vehicular Networks}. In: IEEE Symposium on Computers and Communications (ISCC), 2018.
	
		\section{PRIZES}
			{\sl Science Without Borders}
			\begin{itemize}
				\item[] Recipient of fully-funded scholarship for a year of study abroad in the United States.
			\end{itemize}

		\section{OTHERS}
			{\sl Events}
			\begin{itemize}
				\item[] Participant of Latinoware 2011.
				\item[] Instructor at the Spring 2014 Claremont Colleges Hack Week.
				\item[] Participant of the Claremont Colleges Hackathons of Fall/2013 and Spring/2014.
				\item[] Participant of the regional Southern California International Collegiate Programming Contest.
				\item[] Participant of the Ene Conference in August/2015.
				\item[] Media attendee at E3 2016 in June/2016.
				\item[] Conference author at ISCC 2018 in June/2018.
			\end{itemize}

		\section{HOBBIES \\ AND \\ INTERESTS}
			\begin{itemize}
				\itemsep -2pt
		    	\item Technology \& gadgets
				\item Video games
				\item Film, books and comics
				\item Music (piano and singing)
				\item Photography
				\item Sciences such as astronomy, biology, physics, etc.
			\end{itemize}
	\end{resume}
\end{document}     
ƒ